\documentclass[12pt,answers]{exam}
\usepackage{fontspec,graphicx,caption,circuitikz,amsmath,ragged2e}
\setmainfont{Times New Roman}

\headheight 8pt \headsep 20pt \footskip 30pt
\textheight 9in \textwidth 6.5in
\oddsidemargin 0in \evensidemargin 0in
\topmargin -.35in

\input{assets/defs.tex}

\begin{document}
\begin{center}
\LARGE CSE435 Introduction to EDA \& Testing - Spring 2022 \\
\Large Homework Assignment \#3 \\
\Large Shao-Hsuan Chu - B073040018 \\
\end{center}
\bigskip

\begin{questions}
  \question (20\%) For a D F/F of the following truth table, try to derive a set of function pattern to test this F/F. What functional fault can be detected by your derived pattern.
  \input{assets/dff.tex}
  \begin{solution}
  % \input{solutions/q1.tex}
  \end{solution}

  \question (20\%) For a T F/F of the following truth table, try to derive a set of function pattern to test this F/F. What functional fault can be detected by your derived pattern.
  \input{assets/tff.tex}
  \begin{solution}
  % \input{solutions/q2.tex}
  \end{solution}

  \question (20\%) For a J-K F/F of the following truth table, try to derive a set of function pattern to test this F/F. What functional fault can be detected by your derived pattern.
  \input{assets/jkff.tex}
  \begin{solution}
  % \input{solutions/q3.tex}
  \end{solution}

  \question PLA Faults, Given f1=AB+BC+CA+$\overline{\text{A}}\,\overline{\text{B}}$+$\overline{\text{B}}\,\overline{\text{C}}$+$\overline{\text{C}}\,\overline{\text{A}}$, f2=AB+BC+CA. \\
(20\%) Please draw AND-Array and OR-Array of Missing Crosspoint Faults in AND-OR Plane, and show the equivalent stuck fault representation.
  \begin{parts}
    \part Missing Crosspoint Faults: Missing C in AND Plane.
    \begin{solution}
    % \input{solutions/q4.tex}
    \end{solution}
    \part Missing Crosspoint Faults: Missing {P1, P3, P5} in f1 in OR Plane.
    \begin{solution}
    % \input{solutions/q4.tex}
    \end{solution}
  \end{parts}

  \question PLA Faults, Given f1=AB+BC+CA, f2=$\overline{\text{A}}\,\overline{\text{B}}$+$\overline{\text{B}}\,\overline{\text{C}}$+$\overline{\text{C}}\,\overline{\text{A}}$. \\
  (20\%) Please draw AND-Array and OR-Array of Extra Crosspoint Faults in AND-OR Plane, and show the equivalent stuck fault representation.
  \begin{parts}
    \part Extra Crosspoint Faults: Extra $\overline{\text{B}}$ in P1, A in P2, C in P3 in AND Plane.
    \begin{solution}
    % \input{solutions/q4.tex}
    \end{solution}
    \part Extra Crosspoint Faults: Extra {P4, P5, P6} in f2 in OR Plane.
    \begin{solution}
    % \input{solutions/q4.tex}
    \end{solution}
  \end{parts}
\end{questions}
\end{document}

